---
title: "SOTA 2017-18, stats for Annette"
date: "V1, last updated January 9, 2019"
output: github_document
  #pdf_document: default
  #html_document: default
  #html_document: keep_md: true

always_allow_html: yes
#classoption: landscape

# header-includes:
#     - \usepackage {hyperref}
#     - \hypersetup {colorlinks = true, linkcolor = blue, urlcolor = blue}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align="center", tab.align = "center",
                      fig.width = 7, fig.height = 4)
library(DBI)
myconn <- dbConnect(odbc::odbc(), 
                    Driver = "SQL Server",
                    Server="artlook-production.cw6sjshf3ncd.us-east-2.rds.amazonaws.com",
                    Database = "artlook-production",
                    UID = "launchpadlab",
                    PWD = "Launchpad1",
                    Port = 1433)
```

```{r packages, include = FALSE}
library(knitr)
library(kableExtra)
#library(shiny)
source("I:/Emily/SOTA/sota1718_stats/scripts/sota_schools_format.R")
source("I:/Emily/SOTA/sota1718_stats/scripts/network_spread.R")
```

### Things to know

* Key points for each section will be indicated with a <span style = "color:rgb(46, 184, 46)">"Takeways"</span> header. The basis of the prose describing the data can be built around these.
* More detailed numbers are available upon request (e.g.  tables of what's shown in figures).
* The status of sections will be updated as they are ready to write:
    + "Ready to write" - self-explanatory
    + "In progress" - writing can begin, but numbers may slightly change or a figure may be added
    + "TBA" - analysis in progress on the back end; no content currently available
* Table numbers are way off right now; don't worry about it.    

__Known issues (for Emily):__

* Partnerships - pending programs: Need to fix program types from pending partners
* Network considerations: Should AUSL/ISP also be split by HS/ES?
* Network outliers: How should combo schools be handled? New networks lump ES and HS together.

### Table of Contents {#toc}
* [Section I: Key Findings (TBA)](#section 1)
* [Section II: Arts Ed Plan Goals (TBA)](#section2)
* [Section III: District Information (all ready to write)](#section3)  
    + [III-A: Survey Participation](#participation)
    + [III-A: Creative Schools Certifications](#certification)
    + [III-B: Staffing](#staffing)
    + [III-C: Minutes of Instruction](#minutes)
    + [III-D: Access](#access)
    + [III-E: Disciplines and Depth](#disciplines)
    + [III-F: Additional Arts Assets](#assets)
* [Section IV: Partnerships (mixed)](#section4)
    + [IV-A: Partnership distribution (mostly ready to write, one TBA analysis)](#partnerDistrib)
    + [Iv-B: Programming (in progress)](#partnerProg)
* [Section V: Network Analyses (TBA)](#section5)
* [Section VI: Funding (TBA)](#section6)
* [Section VII: Conclusion (TBA)](#section7)

\newpage
### Section I: Key Findings {#section1}

[Jump back to top](#toc)

<span style="color:red">TBA</span>

```{r test}

plot(1:3, cex = 3, pch = 16, col = "red")
```


***********
***********

### Section II: Arts Ed Plan Goals {#section2}

[Jump back to top](#toc)

<span style="color:red">TBA</span>

***********
***********

\newpage
### Section III: District Information {#section3}

[Jump back to top](#toc)

* Number of Schools: __`r numSchools1718`__
    + Elementary Schools: __`r numES1718`__
    + High Schools: __`r numHS1718`__
* Number of K-12 Students (per CPS 20th day membership file): __`r enrollment_total`__


```{r school numbers summary, include = FALSE}

 kable(school_numbers, caption = "Table 1: Count of schools by Group") %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

```

***********

#### III-A: Creative Schools Survey Participation {#participation}
[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__  
</span>
<span style = "color:rgb(46, 184, 46)">

* District-wide, nearly same participation level as previous year (96% vs. 97%).  
* 100% participation from district-run schools (first time ever!)  
* A drop in charter/contract/options participation.  
</span>

********

```{r participation: district overall}
kable(comp_rate, caption = "Table 2: Survey completion rate by year, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

comp_rate_bar +
  ggtitle("Survey completion rate by year, district overall")

```

***********

```{r participation: es and hs, fig.width = 10}
kable(comp_rate_type, caption = "Table 3: Survey completion rate by year, ES and HS") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

comp_rate_type_bar +
  ggtitle("Survey completion rate by year, ES and HS")

```

***********

```{r participation: district, charter, other, fig.width = 14}
kable(comp_rate_other, caption = "Table 4: Survey completion rate by year: District-run, Charter, Options") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

comp_rate_other_bar +
  ggtitle("Survey completion rate by year: District-run, Charter, Options")
```

```{r participation: network breakdown, include = FALSE}
datatable(comp_rate_net, caption = "Table 5: Survey completion rate by year: Network breakdown",
          rownames = FALSE, options = list(
  pageLength = 95
))
```

********
********


\newpage
#### III-A: Creative Schools Certifications {#certification}
[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__  

 * Small drop in Excelling schools (40% vs. 43% in 2016-17).  
 * High schools are improving, drop comes in from elementary schools.  
 * Bigger drop in charter/contract than district-run CSCs.  
</span>

********

```{r csc: district overall, fig.height = 6, fig.width = 8}
kable(final, caption = "Table 6: Creative Schools Certifications, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

final_csc_plot +
  ggtitle("Creative Schools Certifications, district overall")

```


*****

```{r csc: elementary schools and high schools, fig.height = 8, fig.width = 14}
kable(final_type_es, caption = "Table 7: Creative Schools Certifications, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

kable(final_type_hs, caption = "Table 8: Creative Schools Certifications, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))


final_type_csc_plot +
  ggtitle("Creative Schools Certifications, elementary and high schools")

```

*****

```{r csc: district, charer, options, fig.height = 8, fig.width = 18}
kable(final_districtrun, caption = "Table 9: Creative Schools Certifications, district-run schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

kable(final_charter, caption = "Table 10: Creative Schools Certifications, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

kable(final_options, caption = "Table 11: Creative Schools Certifications, other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

final_other_csc_plot +
   ggtitle("Creative Schools Certifications, network group")

```

*****

```{r csc: network breakdown, fig.width = 25, fig.height = 20, include = FALSE}
datatable(final_net, 
          caption = "Table 12: Creative Schools Certifications, network breakdown",
          rownames = FALSE, options = list(pageLength = 15)
)

# final_net_csc_plot  + 
#   ggtitle("Creative Schools Certifications, network breakdown")
```

#### III-B: Staffing {#staffing}

[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__   

 * Small drop in FTEs from previous year.  
 * Elementary schools commonly have 1 - 2.5 FTE.High schools have a bigger range; one-third of HS have 4 or more FTE. This pattern is stable over time. 
 * Visual arts, music continue to be most common staffing categories.  
 * 0 FTE are slightly on the rise in elementary schools, options schools. 
 * Overall the district has met the 1:350 staffing ratio, but not all schools have. HS are closest (88%), options are weakest (63%) on this metric.
</span>

In order to meet the 1:350 staffing ratio district-wide, CPS would have to employ `r enrollment_total` / 350 = __`r minFTEcount`__ arts instructors.

******

```{r staffing: district count}
kable(staff_count, caption = "Table 13: FTE Count, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

staff_count_bar +
  ggtitle("FTE Count, district overall")
```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district. Due to a lower response rate on the CSS in its first year, satffing totals for 2012-13 are based only on data from CPS Office of Accountability arts staffing files as of June 15, 2013.

*****

```{r staffing: staffing bands, fig.width = 10}

# kable(staff_labels, caption = "Table 14: FTE Bands, ES v HS") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

datatable(staff_labels, 
          caption = "Table 14: FTE Bands, ES v HS",
          rownames = FALSE, options = list(pageLength = 12)
)


staff_bands_bar + ggtitle("FTE Bands, ES v HS")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey

*****

```{r staffing: staffing by arts discipline, district overall}

#kable(teachers_agg, 
#      caption = "Table 15: Staffing by arts discipline, district overall") %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed",
#                                      "responsive", "bordered"))

# disc_time_bar + ggtitle("Staffing by arts discipline by year, district overall")

disc_perc_bar + ggtitle("Staffing by arts discipline, district overall")

```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district.

*****

```{r staffing: staffing by arts discipline by ES/HS}

# kable(teachers_agg_schooltype, 
#       caption = "Table 16: Staffing by arts discipline, by school type") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
#                                       "responsive", "bordered"))

datatable(teachers_agg_schooltype, 
          caption = "Table 16: Staffing by arts discipline, by school type",
          rownames = FALSE, options = list(pageLength = 10)
)
```

```{r staffing by disc by ES/HS figure, fig.width = 12}
disc_type_bar +
  ggtitle("Staffing by arts discipline, by school type, 2017-18")
```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district.

*****

```{r staffing: district overall, fig.height = 5, fig.width = 8}

kable(staff, 
      caption = "Table 17: Staffing categories, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed",
                                      "responsive", "bordered"))

staff_plot +
  ggtitle("Staffing categories, district overall")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey

*****

```{r staffing: elementary schools, include = FALSE}
kable(staff_type_es, 
      caption = "Table 18: Staffing categories, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 6650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey. This is why, for example, the table lists 478 elementary schools for SY 2016-17.

```{r staffing: high schools,  include = FALSE}
kable(staff_type_hs, caption = "Table 19: Staffing categories, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r staffing: categories with 0 FTE, fig.width = 12, fig.height = 6, fig.align = "center"}
zero_fte_type_bar + 
  ggtitle("Staffing categories: Schools with 0 FTE by ES/HS")

zero_fte_group_bar +
  ggtitle("Staffing categories: Schools with 0 FTE by Network Group")
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey. This is why, for example, the table lists 153 high schools for SY 2016-17.

**********

```{r staffing ratio: district overall}
kable(ratio, caption = "Table 20: Staffing ratios, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

**********

```{r staffing ratio: elementary}
kable(ratio_type_es, caption = "Table 21: Staffing ratios, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.

```{r staffing ratio: high school}
kable(ratio_type_hs, caption = "Table 22: Staffing ratios, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.

**********

```{r staffing ratio: district-run}
kable(ratio_districtrun, caption = "Table 23: Staffing ratios, district-run schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: charter}
kable(ratio_charter, caption = "Table 24: Staffing ratios, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: other}
kable(ratio_options, caption = "Table 25: Staffing ratios, other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: network breakdown, include = FALSE}
datatable(ratio_net, caption = "Table 26: Staffing ratios, network breakdown",
          rownames = FALSE, options = list(pageLength = 10))
```

<!--
Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.
-->

*********
*********


\newpage
#### III-C: Minutes of Instruction, Elementary Schools {#minutes}

[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)"> 
__Takeaways:__

* Drop in strong/excelling scores in minutes of instruction this year.  
* Drop seen in both district-run and charter/contract schools. 
</span>

*********

```{r minutes: district overall}
kable(minutes, caption = "Table 27: Minutes of Instruction, district overall") %>%
  kable_styling(bootstrap_options =
                  c("striped", "hover", "condensed", "responsive", "bordered"))

minutes_plot + ggtitle("Minutes of Instruction, district overall")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

*****

```{r minutes: groupings, include = FALSE}
# kable(minutes_other, caption = "Table 28: Minutes of Instruction, groupings") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
#                                       "responsive", "bordered"))

datatable(minutes_other, 
          caption = "Table 28: Minutes of instruction, network type groupings",
          rownames = FALSE, options = list(pageLength = 10))

```

```{r minutes: groupings plot, fig.width = 13, fig.height = 7}
minutes_dcco_plot + ggtitle("Minutes of Instruction by Network Group")
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

*********
*********


\newpage
#### III-D: Percent Access, Elementary Schools {#access}

[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__

* Access across grades is also on a downward trend. 
* 7% fewer schools achieving Excelling this year.  
</span>


```{r percent access: district overall, fig.height = 5}
kable(access, caption = "Table 29: Percent Access") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
  
access_plot + ggtitle("Percent Access, district overall")  
  
```

*********

```{r percent access: by network group, include = FALSE}

# kable(access_other, caption = "Table 29: Percent Access") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

datatable(access_other, 
          caption = "Table 30: Percent Access, network breakdown",
          rownames = FALSE, options = list(pageLength = 10))

```

```{r percent access: by network group plot,  fig.width = 12, fig.height = 5}

access_dcco_plot + ggtitle("Percent Access by Network Group")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

*********
*********


\newpage
#### III-E: Disciplines & Depth, High Schools {#disciplines}

[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__

* Disciplines & Depth upswing: 5% more schools receiving a Strong rating than 2016-17.  
* Improvement driven largely by district-run schools. </span>

```{r disciplines: district overall, fig.height = 5}

kable(disciplines, caption = "Table 30: HS Disciplines and Depth, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed",
                                      "responsive", "bordered"))

disciplines_plot + ggtitle("HS Disciplines and Depth, district overall")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

*****

```{r disciplines: district-run}
kable(disciplines_districtrun, caption = "Table 31: HS Disciplines and Depth, district-run") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: charter}
kable(disciplines_charter, caption = "Table 32: HS Disciplines and Depth, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: options}
kable(disciplines_options, caption = "Table 33: HS Disciplines and Depth, options/other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: plot by network group, fig.width = 15, fig.height = 7}

disciplines_dcco_plot + ggtitle("HS Disciplines and Depth by network group")

```

*****
*****


\newpage
#### III-F: Additional Arts Assets {#assets}

[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__

* Assets mostly stable across time.  
* Some improvement/recovery in professional development, esp. in HS.  
* Something of a downward trend in Budget over the years. </span>

```{r asset plots, all schools, fig.width = 12, fig.height = 4}

asset_all_bar +
  ggtitle("Percentage of schools with additional arts assets, district-wide")

```

```{r asset plots, es v hs, fig.width = 12, fig.height = 8}

asset_es_hs_bar +
  ggtitle("Percentage of schools with additional arts assets, ES v. HS")

```

******
<!--

##### Budget

```{r assets: budget, all schools}
kable(budget, 
      caption = "Table 34: Does the school have a dedicated budget for the arts? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: budget, elementary}
kable(budget_es, caption = "Table 35: Does the school have a dedicated budget for the arts? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: budget, high school}
kable(budget_hs, caption = "Table 36: Does the school have a dedicated budget for the arts? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.


******

##### Arts Integration

```{r assets: artsint, all schools}
kable(artsint, caption = "Table 37: Does the use arts integration strategies? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: artsint, elementary}
kable(artsint_es, caption = "Table 38: Does the use arts integration strategies? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: artsint, high schools}
kable(artsint_hs, caption = "Table 39: Does the use arts integration strategies? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

******

##### Professional Development

```{r assets: profdev, all schools}
kable(profdev, caption = "Table 40: Do teachers at the school have access to arts-specific professional development? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: profdev, elementary}
kable(profdev_es, caption = "Table 41: Do teachers at the school have access to arts-specific professional development? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: profdev, high schools}
kable(profdev_hs, caption = "Table 42: Do teachers at the school have access to arts-specific professional development? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

******

##### Partnerships

```{r assets: part, all schools}
kable(part, caption = "Table 43: Does the school have at least one partnership with an external arts partner? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: part, elementary}
kable(part_es, caption = "Table 44: Does the school have at least one partnership with an external arts partner? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: part, high schools}
kable(part_hs, caption = "Table 45: Does the school have at least one partnership with an external arts partner? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

******

##### Community Engagement

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, all schools}
kable(eng, caption = "Table 46: Does the school have opportunities for parent and community engagement in the arts? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, elementary}
kable(eng_es, caption = "Table 47: Does the school have opportunities for parent and community engagement in the arts? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, high schools}
kable(eng_hs, caption = "Table 48: Does the school have opportunities for parent and community engagement in the arts? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

-->

********
********
********

\newpage
### Section IV: Partnerships {#section4}

[Jump back to top](#toc)

#### IV-A: Partnership distribution {#partnerDistrib}


[Jump back to top](#toc)

<span style = "color:rgb(46, 184, 46)">
__Takeaways:__

* Small bump in number of partners over last year.  
* Small increase in average # of partners per school.  
* Program types: Field trips, resources continue to grow; other categories (besides "other") largely stable.  <span style = "color:red">Numbers to be updated slightly.</span>
* Partner disciplines: music, visual arts most common; some growth in literary arts.
</span>

```{r partnerships: count}

kable(partner_count, 
      caption = "Table 49: Partner Count", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed",
                                      "responsive", "bordered"))

partner_count_bar + ggtitle("Partner count, district-wide")
```

*****

```{r partnerships: average per school}
kable(partner_mean, caption = "Table 50: Average Number of Arts Partners per School", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))


partner_mean_bar + ggtitle("Average Number of Arts Partners per School")

```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

*****

```{r partnerships: partners per school, network breakdown, include = FALSE}
datatable(partner_networks, caption = "Table 51: Active arts partners per school, network breakdown",
          rownames = FALSE, options = list(
  pageLength = 10
))
```

```{r partnerships: network breakdown plot, include = FALSE, fig.height = 15, fig.width = 18}

partner_net_bar + ggtitle("Active arts partners per school, network breakdown")

```

*****

```{r partnerships: partner disciplines by year, fig.height = 6, fig.width = 8}

# kable(disc_agg, 
# caption = "Table 53: Arts partner disciplines by year", row.names = FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
#   "responsive", "bordered"))

partner_disc_bar + ggtitle("Arts partner disciplines")
  
```

Note: partnership organizations may identify with more than one arts discipline, so total disciplines may add up to more than 100%.

#### Some sort of broader partner analysis will go here (TBA)

<span style = "color:red">TBA. This section will include:

 * Geographic trends, or
 * Partners in 17-18 meeting requests from 16-17, or
 * Geographic distribution of programmign types (to go in IV-B)
</span> 
 
#### IV-B: Partnership programming {#partnerProg}  
 

[Jump back to top](#toc) 
 
```{r partnerships: program type count, fig.height = 6, fig.width = 8}
# kable(program_types, caption = "Table 52: Arts program types", row.names = FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))

program_types_bar + ggtitle("Arts program types")

```
 
\newpage
### Section 5: Network Analyses {#section5}

[Jump back to top](#toc)

<span style = "color:red">TBA</span>

```{r network_spread_intro, fig.width = 14, fig.height = 12}

#net_csc_bar

```

\newpage
### Section 6: Funding {#section6}

[Jump back to top](#toc)

<span style = "color:red">TBA</span>

\newpage
### Section 7: Conclusion {#section7}

[Jump back to top](#toc)

<span style = "color:red">TBA</span>