---
title: "State of the Arts in Chicago Public Schools 2017-18 - V3"
output: html_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DBI)
myconn <- dbConnect(odbc::odbc(), 
                    Driver = "SQL Server",
                    Server="artlook-production.cw6sjshf3ncd.us-east-2.rds.amazonaws.com",
                    Database = "artlook-production",
                    UID = "launchpadlab",
                    PWD = "Launchpad1",
                    Port = 1433)
```

```{r packages, include = FALSE}
library(knitr)
library(kableExtra)
library(shiny)
source("I:/Data & Impact/Analyses/State of the Arts in Chicago Public Schools/scripts/sota_schools_format.R")
```

### District Information
* Number of Schools: __650__
    + Elementary Schools: __480__
    + High Schools: __170__
* Number of K-12 Students (per CPS' 20th day membership file): __352,654__


```{r school numbers summary}
kable(school_numbers, caption = "Table 1: Count of schools by Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

### Creative Schools Survey Participation

```{r participation: district overall}
kable(comp_rate, caption = "Table 2: Survey completion rate by year, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r participation: es and hs}
kable(comp_rate_type, caption = "Table 3: Survey completion rate by year, ES and HS") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r participation: district, charter, other}
kable(comp_rate_other, caption = "Table 4: Survey completion rate by year: District-run, Charter, Options") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r participation: network breakdown}
datatable(comp_rate_net, caption = "Table 5: Survey completion rate by year: Network breakdown",
          rownames = FALSE, options = list(
  pageLength = 95
))
```

### Creative Schools Certifications

```{r csc: district overall}
kable(final, caption = "Table 6: Creative Schools Certifications, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: elementary schools}
kable(final_type_es, caption = "Table 7: Creative Schools Certifications, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: high schools}
kable(final_type_hs, caption = "Table 8: Creative Schools Certifications, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: district-run}
kable(final_districtrun, caption = "Table 9: Creative Schools Certifications, district-run schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: charter}
kable(final_charter, caption = "Table 10: Creative Schools Certifications, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: other}
kable(final_options, caption = "Table 11: Creative Schools Certifications, other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r csc: network breakdown}
datatable(final_net, caption = "Table 12: Creative Schools Certifications, network breakdown",
          rownames = FALSE, options = list(
  pageLength = 50
))
```

### Staffing

In order to meet the 1:350 staffing ration distirct wide, CPS would have to employ 356,675 / 350 = 1,007 arts instructors.

```{r staffing: district count}
kable(staff_count, caption = "Table 13: FTE Count, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district.

```{r staffing: staffing bands}
kable(staff_labels, caption = "Table 14: FTE Bands, ES v HS") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey

```{r staffing: staffing by arts discipline, district overall}
kable(teachers_agg, caption = "Table 15: Staffing by arts discipline, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district.

```{r staffing: staffing by arts discipline, by school type}
kable(teachers_agg_schooltype, caption = "Table 16: Staffing by arts discipline, by school type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: Data sources for this table include the Creative Schools Survey and CPS staffing files. This table, therefore, captures arts staff that existed in any of CPS' "school units" for a given year (i.e., 666 for 2017-18). Considering data from both reporting and non-reporting schools provides a more complete picture of arts staffing across the district.

```{r staffing: district overall}
kable(staff, caption = "Table 17: Staffing categories, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey

```{r staffing: elementary schools}
kable(staff_type_es, caption = "Table 18: Staffing categories, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 6650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey. This is why, for example, the table lists 478 elementary schools for SY 2016-17.

```{r staffing: high schools}
kable(staff_type_hs, caption = "Table 19: Staffing categories, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only includes those schools that completed a Creative Schools Survey. This is why, for example, the table lists 153 high schools for SY 2016-17.

```{r staffing ratio: district overall}
kable(ratio, caption = "Table 20: Staffing ratios, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: elementary}
kable(ratio_type_es, caption = "Table 21: Staffing ratios, elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.

```{r staffing ratio: high school}
kable(ratio_type_hs, caption = "Table 22: Staffing ratios, high schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.

```{r staffing ratio: district-run}
kable(ratio_districtrun, caption = "Table 23: Staffing ratios, district-run schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: charter}
kable(ratio_charter, caption = "Table 24: Staffing ratios, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: other}
kable(ratio_options, caption = "Table 25: Staffing ratios, other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include schools that completed the Creative Schools Survey.

```{r staffing ratio: network breakdown}
datatable(ratio_net, caption = "Table 26: Staffing ratios, network breakdown",
          rownames = FALSE, options = list(
  pageLength = 50
))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and include Category 5 schools.

### Minutes of Instruction

```{r minutes: district overall}
kable(minutes, caption = "Table 27: Minutes of Instruction, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r minutes: groupings}
kable(minutes_other, caption = "Table 28: Minutes of Instruction, groupings") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

### Percent Access
```{r percent access: district overall}
kable(access, caption = "Table 29: Percent Access") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

### Disciplines & Depth
```{r disciplines: district overall}
kable(disciplines, caption = "Table 30: HS Disciplines & Depth, district overall") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: district-run}
kable(disciplines_districtrun, caption = "Table 31: HS Disciplines & Depth, district-run") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: charter}
kable(disciplines_charter, caption = "Table 32: HS Disciplines & Depth, charter and contract schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r disciplines: options}
kable(disciplines_options, caption = "Table 33: HS Disciplines & Depth, other school types") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

### Additional Arts Assets

```{r assets: budget, all schools}
kable(budget, caption = "Table 34: Does the school have a dedicated budget for the arts? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: budget, elementary}
kable(budget_es, caption = "Table 35: Does the school have a dedicated budget for the arts? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: budget, high school}
kable(budget_hs, caption = "Table 36: Does the school have a dedicated budget for the arts? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: artsint, all schools}
kable(artsint, caption = "Table 37: Does the use arts integration strategies? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: artsint, elementary}
kable(artsint_es, caption = "Table 38: Does the use arts integration strategies? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: artsint, high schools}
kable(artsint_hs, caption = "Table 39: Does the use arts integration strategies? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: profdev, all schools}
kable(profdev, caption = "Table 40: Do teachers at the school have access to arts-specific professional development? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: profdev, elementary}
kable(profdev_es, caption = "Table 41: Do teachers at the school have access to arts-specific professional development? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: profdev, high schools}
kable(profdev_hs, caption = "Table 42: Do teachers at the school have access to arts-specific professional development? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: part, all schools}
kable(part, caption = "Table 43: Does the school have at least one partnership with an external arts partner? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: part, elementary}
kable(part_es, caption = "Table 44: Does the school have at least one partnership with an external arts partner? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: part, high schools}
kable(part_hs, caption = "Table 45: Does the school have at least one partnership with an external arts partner? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, all schools}
kable(eng, caption = "Table 46: Does the school have opportunities for parent and community engagement in the arts? All schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, elementary}
kable(eng_es, caption = "Table 47: Does the school have opportunities for parent and community engagement in the arts? Elementary schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r assets: engagement, high schools}
kable(eng_hs, caption = "Table 48: Does the school have opportunities for parent and community engagement in the arts? High schools") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

### Partnerships
```{r partnerships: count}
kable(partner_count, caption = "Table 49: Partner Count", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r partnerships: average per school}
kable(partner_mean, caption = "Table 50: Average Number of Arts Partners per School", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

Note: These data are calculated from the "condensed" rubrics (i.e., 650 schools for SY 2017-18) and only include those schools that responded to the survey.

```{r partnerships: partners per school, network breakdown}
datatable(partner_networks, caption = "Table 51: Active arts partners per school, network breakdown",
          rownames = FALSE, options = list(
  pageLength = 50
))
```

```{r partnerships: program type count}
kable(program_types, caption = "Table 52: Arts program types", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```

```{r partnerships: partner disciplines by year}
kable(disc_agg, caption = "Table 53: Arts partner disciplines by year", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"))
```
